```{r}
if (!exists("section1_title")) section1_title <- "Best / Worst"
if (!exists("section1_metrics")) section1_metrics <- c("Best", "Worst")
if (!exists("section2_title")) section2_title <- "Most / Least Polarizing"
if (!exists("color_by")) color_by <- "bookmaker"
if (!exists("meta")) meta <- NA
```

# `r title`
## `r section1_title` {.tabset}
### Pre-`r params$year`

`r section1_metrics[1]`: `r get_result_value("previous", dataset, "average", "best")`

`r section1_metrics[2]`: `r get_result_value("previous", dataset, "average", "worst")`

```{r}
make_bar_plot(
  get(dataset),
  group,
  "average",
  color = color_by,
  timeframe = "previous",
  meta = meta
)
```
### `r params$year`

`r section1_metrics[1]`: `r get_result_value("current", dataset, "average", "best")`

`r section1_metrics[2]`: `r get_result_value("current", dataset, "average", "worst")`

```{r}
make_bar_plot(
  get(dataset),
  group,
  "average",
  color = color_by,
  timeframe = "current",
  meta = meta
)
```
### All

`r section1_metrics[1]`: `r get_result_value("all", dataset, "average", "best")`

`r section1_metrics[2]`: `r get_result_value("all", dataset, "average", "worst")`

```{r}
make_bar_plot(
  get(dataset),
  group,
  "average",
  color = color_by,
  timeframe = "all",
  meta = meta
)
```

## `r section2_title` {.tabset}
### Pre-`r params$year`
Most: `r get_result_value("previous", dataset, "stdev", "best")`

Least: `r get_result_value("previous", dataset, "stdev", "worst")`

```{r}
make_bar_plot(
  get(dataset),
  group,
  "stdev",
  color = color_by,
  timeframe = "previous",
  meta = meta
)
```
### `r params$year`
Most: `r get_result_value("current", dataset, "stdev", "best")`

Least: `r get_result_value("current", dataset, "stdev", "worst")`

```{r}
make_bar_plot(
  get(dataset),
  group,
  "stdev",
  color = color_by,
  timeframe = "current",
  meta = meta
)
```
### All
Most: `r get_result_value("all", dataset, "stdev", "best")`

Least: `r get_result_value("all", dataset, "stdev", "worst")`

```{r}
make_bar_plot(
  get(dataset),
  group,
  "stdev",
  color = color_by,
  timeframe = "all",
  meta = meta
)
```
<!-- TODO: Move additional chunks to their own files and add them as a paramter in the analysis list -->
```{r, eval = (dataset == "raters") & (params$year > 2020), results = "asis"}
cat("## Favorite / Least Favorite Bookmaker", sep = "\n")
```
```{r, eval = (dataset == "raters") & (params$year > 2020)}
# Note: all time only
max_values <- raters_bookmakers == apply(raters_bookmakers, 1, max)
min_values <- raters_bookmakers == apply(raters_bookmakers, 1, min)

df <- raters_bookmakers %>%
  mutate(across(where(is.numeric), sprintf, fmt = "%.2f"))

for (i in seq_along(df)) {
  for (j in seq_along(df)) {
    if (min_values[i, j]) {
      bg_color <- "#67a9cf"
    } else if (max_values[i, j]) {
      bg_color <- "#ef8a62"
    } else {
      bg_color <- "#FFFFFF"
    }
    df[i, j] <- cell_spec(
      df[i, j],
      format =  "html",
      background = bg_color,
      underline = i == j
    )
  }
}

df %>%
  kable(format = "html", escape = FALSE, booktabs = TRUE) %>%
  kable_styling() %>%
  add_header_above(c(" " = 1, "Bookmaker" = ncol(df)))
```

```{r, eval = (dataset == "books"), results = "asis"}
cat("## Rating groups", sep = "\n")
```
```{r, eval = (dataset == "books")}
df <- get(dataset) %>%
  filter(timeframe == "all") %>%
  mutate(
    group = paste(grp_cons, grp_like)
  )
df_current <- df %>%
  filter(year == params$year) %>%
  mutate(
    ax = sample(c(-30:-15, 15:30), n()),
    ay = sample(c(-30:-15, 15:30), n())
  )

get_mid_points <- function(values) {
  five_num <- summary(values)
  list(
    min = five_num[[1]],
    lower = mean(five_num[c(1, 3)]),
    upper = mean(five_num[c(3, 6)]),
    max = five_num[[6]]
  )
}
avg_pos <- get_mid_points(df$average)
std_pos <- get_mid_points(df$stdev)
annotations <- as.data.frame(
  matrix(c(
    c(avg_pos$lower, 0.95 * std_pos$min, "Disliked"),
    c(avg_pos$upper, 0.95 * std_pos$min, "Liked"),
    c(0.95 * avg_pos$min, std_pos$lower, "Universally"),
    c(0.95 * avg_pos$min, std_pos$upper, "Partially")
  ), ncol = 3, byrow = TRUE)
)

default_hovertemplate <- paste0(
  "%{hovertext}<br>",
  "Rating: %{x:.2f}<br>",
  "Std dev: %{y:.2f}"
)
plot_ly(
  df,
  y = ~stdev,
  x = ~average,
  color = ~bookmaker,
  colors = bookmaker_info$color,
  showlegend = FALSE,
  hovertext = ~book,
  hovertemplate = default_hovertemplate,
  name = "",
  type = "scatter",
  mode = "markers"
) %>%
  layout(
    xaxis = list(
      title=list(text="Average rating")
    ),
    yaxis = list(
      title=list(text="Standard deviation")
    )
  ) %>%
  add_annotations(
    data = df_current,
    ay=~ay,
    ax=~ax,
    text=~book,
    arrowhead=0
  ) %>%
  add_segments(
    x = median(df$average),
    xend = median(df$average),
    y = 0.95*min(df$stdev),
    yend = 1.05*max(df$stdev),
    line = list(color = "grey", dash = "dash", width = 0.5),
    showlegend=FALSE
  ) %>%
  add_segments(
    y = median(df$stdev),
    yend = median(df$stdev),
    x = 0.95*min(df$average),
    xend = 1.05*max(df$average),
    line = list(color = "grey", dash = "dash", width = 0.5),
    showlegend=FALSE
  ) %>%
  add_annotations(
    data = annotations,
    y = ~V2,
    x = ~V1,
    text = ~V3,
    textangle = ~if_else(V3 %in% c("Liked", "Disliked"), 0, -90),
    font = list(size=18, style="italic", weight="bold"),
    showarrow = FALSE
  ) %>%
  config(displayModeBar = FALSE)
```