---
title: "Superfriends Book Club"
subtitle: "2023 Wrapped"
output:
  html_document:
    fig_height: 8
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
params:
  year: 2022
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
library(readr)
library(plyr)
library(dplyr)
library(tidyr)
library(plotly)
library(kableExtra)
```

```{r generate-meta-data}
bookmaker_info <- data.frame(
  bookmaker = as.ordered(c(
    "Amanda",
    "Ben",
    "Brandon",
    "Hannah",
    "Healy",
    "Julia",
    "Kevin",
    "Ryan",
    "Sam"
  )),
  color = c(
    "#1f78bf",
    "#b2df8a",
    "#cab2d6",
    "#e31a1c",
    "#ff6d01",
    "#ffff99",
    "#33a02c",
    "#a6cee3",
    "#6a3d9a"
  ),
  pair = c(
    "Ben",
    "Amanda",
    NA,
    "Kevin",
    "Sam",
    "Ryan",
    "Hannah",
    "Julia",
    "Sam"
  )
)
bookmaker_info$pair <- ordered(
  bookmaker_info$pair,
  levels = bookmaker_info$bookmaker
)
bookmaker_info$pair_name <- with(bookmaker_info, {
  if_else(!is.na(pair),
          paste(pmax(bookmaker, pair), "&", pmin(bookmaker, pair)),
          NA_character_)
})
```
```{r generate-ratings}
ratings <- read_csv(
  "data/SF Book Club Ratings - Ratings.csv",
  show_col_types = FALSE) %>%
  select(-`Healy's Recap`, -Average, -SD, -Rating) %>%
  rename(
    date = `Book Club Date`,
    bookmaker = Bookmaker,
    book = Book
  ) %>%
  mutate(
    date = as.Date(date, format="%m/%d/%Y"),
    book = gsub(":.*", "", book)  # Remove subtitles
  ) %>%
  pivot_longer(
    -c(date, bookmaker, book),
    names_to = "rater",
    values_to = "rating"
  ) %>%
  drop_na() %>%
  mutate(
    rating = nchar(rating),
    year = as.integer(format(date, "%Y"))
  ) %>%
  filter(year <= params$year)

ratings$bookmaker <- ordered(
  ratings$bookmaker,
  levels = bookmaker_info$bookmaker
)
ratings$rater <- ordered(ratings$rater, levels = bookmaker_info$bookmaker)

book_to_maker <- ratings %>%
  select(book, bookmaker) %>%
  distinct()
```
```{r make-summaries}
get_ratings_summary <- function(group) {
  all_summary <- ratings %>%
    group_by_at(group) %>%
    dplyr::summarise(
      average = mean(rating),
      stdev = sd(rating),
      n = n(),
      book_count = n_distinct(book)
    ) %>%
    mutate(timeframe = "all")
  current_summary <- ratings %>%
    filter(year == params$year) %>%
    group_by_at(group) %>%
    dplyr::summarise(
      average = mean(rating),
      stdev = sd(rating),
      n = n(),
      book_count = n_distinct(book)
    ) %>%
    mutate(timeframe = "current")
  bind_rows(all_summary, current_summary)
}

bookmakers <- get_ratings_summary("bookmaker")
books <- get_ratings_summary("book") %>%
  join(book_to_maker, by = "book")
raters <- get_ratings_summary("rater")
raters_bookmakers <- get_ratings_summary(c("rater", "bookmaker")) %>%
  filter(rater != "Brandon", bookmaker != "Brandon") %>%
  select(rater, bookmaker, average) %>%
  pivot_wider(names_from = bookmaker, values_from = average) %>%
  as.data.frame()
row.names(raters_bookmakers) <- raters_bookmakers$rater
raters_bookmakers$rater <- NULL

ratings_mat <- ratings %>%
  filter(rater %in% raters$rater[raters$n > 5]) %>%
  select(book, rater, rating) %>%
  pivot_wider(names_from = rater, values_from = rating) %>%
  as.data.frame()
row.names(ratings_mat) <- ratings_mat$book
ratings_mat <- select(ratings_mat, -book)

# TODO: confirm this is working correctly and make this a function
cors <- cor(ratings_mat, use = "pairwise.complete.obs")
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
p.mat <- cor.mtest(ratings_mat)

cors_long <- as.data.frame.table(
    cors,
    responseName = "cor",
    stringsAsFactors = FALSE
  ) %>%
  filter(Var1 > Var2) %>%
  mutate(pair_name = paste(Var1, "&", Var2)) %>%
  select(-Var1, -Var2) %>%
  arrange(-cor)
```
```{r generate-results-data}
get_best_worst <- function(timeframe, dataset, metric, type) {
  df <- get(dataset) %>%
    filter(timeframe == !!timeframe)
  target_value <- ifelse(
    type == "best",
    max(df[metric], na.rm = TRUE),
    min(df[metric], na.rm = TRUE)
  )
  result <- df[df[metric] == target_value, ] %>%
    drop_na(all_of(metric)) %>%
    pull(1)

  paste(result, collapse = " / ")
}

set_result_value <- function(
    value,
    timeframe,
    dataset,
    metric,
    type = NA_character_) {

  new_value <- data.frame(
    timeframe = timeframe,
    dataset = dataset,
    metric = metric,
    type = type,
    value = as.character(value)
  )
  results_df <<- results_df %>%
    rows_upsert(new_value, by = c("timeframe", "dataset", "metric", "type"))
}

results_df <- expand.grid(
  timeframe = c("current", "all"),
  dataset = c("books", "raters", "bookmakers"),
  metric = c("average", "stdev"),
  type = c("best", "worst"),
  value = NA_character_,
  stringsAsFactors = FALSE
)

for (i in seq_len(nrow(results_df))) {
  timeframe <- results_df[i, "timeframe"]
  dataset <- results_df[i, "dataset"]
  metric <- results_df[i, "metric"]
  type <- results_df[i, "type"]

  result <- get_best_worst(timeframe, dataset, metric, type)
  set_result_value(result, timeframe, dataset, metric, type)
}

for (timeframe in c("all", "current")) {
  num_ratings <- ifelse(
    timeframe == "all",
    nrow(ratings),
    filter(ratings, year == params$year) %>% nrow()
  )
  set_result_value(num_ratings, timeframe, "summary", "ratings")

  set_result_value(
    nrow(filter(books, timeframe == !!timeframe)),
    timeframe,
    "summary",
    "books"
  )

  if (timeframe == "all") {
    set_result_value(
      filter(bookmakers, timeframe == "all") %>%
        pull(book_count) %>%
        max(),
      timeframe,
      "summary",
      "cycle"
    )
  }

  if(timeframe == "all") {
    start_date <- min(ratings$date)
  } else {
    start_date <- ratings %>%
      filter(year == params$year) %>%
      pull(date) %>%
      min()
  }
  if(format(Sys.Date(), "%Y") == params$year) {
    end_date <- Sys.Date()
  } else {
    end_date <- as.Date(paste(params$year, "12", "31", sep = "-"))
  }
  set_result_value(
    difftime(end_date, start_date, units = "d"),
    timeframe,
    "summary",
    "days_since"
  )
}

# TODO: Update this for year split
results[["cors"]][["pair"]][["max"]] <- cors_long[[which.max(cors_long$cor),
                                                   "pair_name"]]
results[["cors"]][["pair"]][["min"]] <- cors_long[[which.min(cors_long$cor),
                                                   "pair_name"]]
```

```{r make-functions}
make_bar_plot <- function(df,
                          group,
                          metric,
                          color="bookmaker",
                          show_n=NA) {
  df <- df %>%
    arrange(across(metric, desc))

  xaxis_title <- switch(metric,
    "average" = "Avg Rating",
    "std" = "Std. Deviation"
  )
  
  make_plot <- function(df, title="") {
    plot_ly(
        type="bar",
        y=df[[group]],
        x=df[[metric]],
        color=df[[color]],
        colors = bookmaker_info$color,
        # legendgroup="group1",  # Can't filter to one legend item
        orientation="h"
      ) %>%
      layout(
        yaxis = list(
          categoryorder = "total ascending",
          title = title
        ),
        xaxis = list(title = xaxis_title),
        showlegend = color != group
      )
    }
    
    if(is.na(show_n)) {
      p <- make_plot(df)  
    } else {
      if(2*show_n > nrow(df)) {
        stop("invalid show_n value")
      }
      p1 <- df %>%
        slice_head(n = show_n) %>%
        make_plot(title = paste("Top", show_n))
      p2 <- df %>%
        slice_tail(n = show_n) %>%
        make_plot(title = paste("Bottom", show_n))
      p <- subplot(p1, p2, nrows = 2, shareX = TRUE, titleY = TRUE)
    }
    
    p
}
```

# Summary Data

- Books read: `r results$summary$books`
- Number of ratings: `r results$summary$ratings`
- Current cycle: `r results$summary$cycle`
- Avg days between meetings: `r round(results$summary$days_since / results$summary$books, 0)`

# Books
## Best / Worst

Best: `r results$books$average$best`

Worst: `r results$books$average$worst`

```{r books-ratings}
make_bar_plot(books, "book", "average")
```

## Most / Least Polarizing

Most: `r results$books$stdev$best`

Least: `r results$books$stdev$worst`

```{r books-stdev}
make_bar_plot(books, "book", "stdev")
```

# Bookmakers

## Best / Worst

Best: `r results$bookmakers$average$best`

Worst: `r results$bookmakers$average$worst`

```{r bookmakers-ratings}
make_bar_plot(bookmakers, "bookmaker", "average")
```

## Most / Least Polarizing

Most: `r results$bookmakers$stdev$best`

Least: `r results$bookmakers$stdev$worst`

```{r bookmakers-stdev}
make_bar_plot(bookmakers, "bookmaker", "stdev")
```

# Raters

## Highest / Lowest
Highest: `r results$raters$average$best`

Lowest: `r results$raters$average$worst`

```{r raters-avg}
make_bar_plot(raters, "rater", "average", color="rater")
```

## Most / Least Variable
Most: `r results$raters$stdev$best`

Least: `r results$raters$stdev$worst`

```{r raters-stdev}
make_bar_plot(raters, "rater", "stdev", color="rater")
```

## Favorite / Least Favorite Bookmaker

```{r}
max_values <- raters_bookmakers == apply(raters_bookmakers, 1, max)
min_values <- raters_bookmakers == apply(raters_bookmakers, 1, min)

df <- raters_bookmakers %>%
  mutate(across(where(is.numeric), sprintf, fmt = '%.2f'))

df[max_values] <- cell_spec(df[max_values],
                            format =  "html",
                            background = "#ef8a62")
df[min_values] <- cell_spec(df[min_values],
                            format =  "html",
                            background = "#67a9cf")
df %>%
  kable(format = "html", escape = FALSE, booktabs=TRUE) %>%
  kable_styling() %>%
  add_header_above(c(" "=1, "Bookmaker" = ncol(df)))
```

# Preference Similarity

## Most / Least Similar

Most: `r results$cors$pair$max`

Least: `r results$cors$pair$min`

```{r corr-plot}
mat <- cors
diag(mat) <- NA
max_cors <- apply(mat, 1, max, na.rm = TRUE)
min_cors <- apply(mat, 1, min, na.rm = TRUE)

p <- corrplot::corrplot(
  cors,
  method = 'ellipse',
  order = 'hclust',
  addrect = 2,
  type='full',
  diag=FALSE,
  addCoef.col = "black",
  number.cex = .75,
  tl.col="black",
  tl.pos = 'd',
  tl.cex = 0.75,
  p.mat = mat == max_cors | mat == min_cors,
  insig = "pch",
  pch = 0,
  pch.cex = 5,
  pch.col = "#D3D3D3"
)
```

## Couple & Sibling Pairs
```{r}
df <- cors_long %>%
  filter(pair_name %in% bookmaker_info$pair_name) %>%
  arrange(desc(cor)) %>%
  mutate(cor = scales::label_percent(accuracy=1)(cor))
row.names(df) <- df$Pair
df$Pair <- NULL

df %>%
  kable(col.names = NULL) %>%
  kable_styling(full_width = FALSE)
```
