---
title: "Superfriends Book Club"
subtitle: "2023 Wrapped"
output:
  html_document:
    fig_height: 8
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
library(readr)
library(plyr)
library(dplyr)
library(tidyr)
library(plotly)
library(kableExtra)
```

```{r process-data}
bookmaker_info <- data.frame(
  bookmaker = as.ordered(c("Amanda", "Ben", "Brandon", "Hannah", "Healy", "Julia", "Kevin", "Ryan", "Sam")),
  color = c("#1f78bf", "#b2df8a", "#cab2d6", "#e31a1c", "#ff6d01", "#ffff99", "#33a02c", "#a6cee3", "#6a3d9a"),
  pair = c("Ben", "Amanda", NA, "Kevin", "Sam", "Ryan", "Hannah", "Julia", "Sam")
)
bookmaker_info$pair <- ordered(bookmaker_info$pair, levels = bookmaker_info$bookmaker)
bookmaker_info$pair_name <- with(bookmaker_info, {
  if_else(!is.na(pair),
          paste(pmax(bookmaker, pair), "&", pmin(bookmaker, pair)),
          NA_character_)
})

rating_data <- read_csv("~/Downloads/SF Book Club Ratings - Ratings(3).csv", show_col_types = FALSE)

ratings <- rating_data %>%
  select(-`Healy's Recap`, -Average, -SD, -Rating) %>%
  rename(
    date = `Book Club Date`,
    bookmaker = Bookmaker,
    book = Book
  ) %>%
  mutate(
    date = as.Date(date, format="%m/%d/%Y"),
    book = gsub(":.*", "", book)  # Remove subtitles
  ) %>%
  pivot_longer(
    -c(date, bookmaker, book),
    names_to = "rater",
    values_to = "rating"
  ) %>%
  drop_na() %>%
  mutate(rating = nchar(rating))

ratings$bookmaker <- ordered(ratings$bookmaker, levels = bookmaker_info$bookmaker)
ratings$rater <- ordered(ratings$rater, levels = bookmaker_info$bookmaker)

book_to_maker <- ratings %>%
  select(book, bookmaker) %>%
  distinct()

get_ratings_summary <- function(group) {
  ratings %>%
    group_by_at(group) %>%
    summarise(
      average = mean(rating),
      stdev = sd(rating),
      n = n(),
      book_count = n_distinct(book)
    )
}

bookmakers <- get_ratings_summary("bookmaker")
books <- get_ratings_summary("book") %>%
  join(book_to_maker, by = "book")
raters <- get_ratings_summary("rater")
raters_bookmakers <- get_ratings_summary(c("rater", "bookmaker")) %>%
  filter(rater != "Brandon", bookmaker != "Brandon") %>%
  select(rater, bookmaker, average) %>%
  pivot_wider(names_from = bookmaker, values_from = average) %>%
  as.data.frame()
row.names(raters_bookmakers) <- raters_bookmakers$rater
raters_bookmakers$rater <- NULL

ratings_mat <- ratings %>%
  filter(rater %in% raters$rater[raters$n > 5]) %>%
  select(book, rater, rating) %>%
  pivot_wider(names_from = rater, values_from = rating) %>%
  as.data.frame()
row.names(ratings_mat) <- ratings_mat$book
ratings_mat <- select(ratings_mat, -book)

cors <- cor(ratings_mat, use = "pairwise.complete.obs")
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
p.mat <- cor.mtest(ratings_mat)

cors_long <- as.data.frame.table(cors, responseName = "cor", stringsAsFactors = FALSE) %>%
  filter(Var1 > Var2) %>%
  mutate(pair_name = paste(Var1, "&", Var2)) %>%
  select(-Var1, -Var2) %>%
  arrange(-cor)

get_best_worst <- function(df_name, value, type) {
  df <- get(df_name)
  target_value <- ifelse(type == "best", max(df[value]), min(df[value]))
  result <- df[df[value] == target_value, ] %>%
    pull(1)
  return(result)
}

results_to_build <- expand.grid(
  c("books", "raters", "bookmakers"),
  c("average", "stdev"),
  c("best", "worst"),
  stringsAsFactors = FALSE
)

results <- list()

results[["summary"]] <- list(
  "ratings" = nrow(ratings),
  "books" = nrow(books),
  "cycle" = max(bookmakers$book_count),
  "days_since" = as.numeric(difftime(Sys.Date(), min(ratings$date), units = "d"))
)
  
for(i in 1:nrow(results_to_build)) {
  df_name <- results_to_build[i, "Var1"]
  value <- results_to_build[i, "Var2"]
  type <- results_to_build[i, "Var3"]
  result <- get_best_worst(df = df_name, value = value, type = type)
  results[[df_name]][[value]][[type]] <- result
}

results[["cors"]][["pair"]][["max"]] <- cors_long[[which.max(cors_long$cor),
                                                   "pair_name"]]
results[["cors"]][["pair"]][["min"]] <- cors_long[[which.min(cors_long$cor),
                                                   "pair_name"]]
```

```{r make-functions}
make_bar_plot <- function(df,
                          group,
                          metric,
                          color="bookmaker",
                          show_n=NA) {
  df <- df %>%
    arrange(across(metric, desc))

  xaxis_title <- switch(metric,
    "average" = "Avg Rating",
    "std" = "Std. Deviation"
  )
  
  make_plot <- function(df, title="") {
    plot_ly(
        type="bar",
        y=df[[group]],
        x=df[[metric]],
        color=df[[color]],
        colors = bookmaker_info$color,
        # legendgroup="group1",  # With this, you can't filter to one legend item
        orientation="h"
      ) %>%
      layout(
        yaxis = list(
          categoryorder = "total ascending",
          title = title
        ),
        xaxis = list(title = xaxis_title),
        showlegend = color != group
      )
    }
    
    if(is.na(show_n)) {
      p <- make_plot(df)  
    } else {
      if(2*show_n > nrow(df)) {
        stop("invalid show_n value")
      }
      
      p1 <- df %>%
        slice_head(n = show_n) %>%
        make_plot(title = paste("Top", show_n))
      
      p2 <- df %>%
        slice_tail(n = show_n) %>%
        make_plot(title = paste("Bottom", show_n))
      
      p <- subplot(p1, p2, nrows = 2, shareX = TRUE, titleY = TRUE)
    }
    
    p
}
```

# Summary Data

- Books read: `r results$summary$books`
- Number of ratings: `r results$summary$ratings`
- Current cycle: `r results$summary$cycle`
- Avg days between meetings: `r round(results$summary$days_since / results$summary$books, 0)`

# Books
## Best / Worst

Best: `r results$books$average$best`

Worst: `r results$books$average$worst`

```{r books-ratings}
make_bar_plot(books, "book", "average")
```

## Most / Least Polarizing

Most: `r results$books$stdev$best`

Least: `r results$books$stdev$worst`

```{r books-stdev}
make_bar_plot(books, "book", "stdev")
```

# Bookmakers

## Best / Worst

Best: `r results$bookmakers$average$best`

Worst: `r results$bookmakers$average$worst`

```{r bookmakers-ratings}
make_bar_plot(bookmakers, "bookmaker", "average")
```

## Most / Least Polarizing

Most: `r results$bookmakers$stdev$best`

Least: `r results$bookmakers$stdev$worst`

```{r bookmakers-stdev}
make_bar_plot(bookmakers, "bookmaker", "stdev")
```

# Raters

## Highest / Lowest
Highest: `r results$raters$average$best`

Lowest: `r results$raters$average$worst`

```{r raters-avg}
make_bar_plot(raters, "rater", "average", color="rater")
```

## Most / Least Variable
Most: `r results$raters$stdev$best`

Least: `r results$raters$stdev$worst`

```{r raters-stdev}
make_bar_plot(raters, "rater", "stdev", color="rater")
```

## Favorite / Least Favorite Bookmaker

```{r}
max_values <- raters_bookmakers == apply(raters_bookmakers, 1, max)
min_values <- raters_bookmakers == apply(raters_bookmakers, 1, min)

df <- raters_bookmakers %>%
  mutate(across(where(is.numeric), sprintf, fmt = '%.2f'))

df[max_values] <- cell_spec(df[max_values],
                            format =  "html",
                            background = "#ef8a62")
df[min_values] <- cell_spec(df[min_values],
                            format =  "html",
                            background = "#67a9cf")
df %>%
  kable(format = "html", escape = FALSE, booktabs=TRUE) %>%
  kable_styling() %>%
  add_header_above(c(" "=1, "Bookmaker" = ncol(df)))
```

# Preference Similarity

## Most / Least Similar

Most: `r results$cors$pair$max`

Least: `r results$cors$pair$min`

```{r corr-plot}
mat <- cors
diag(mat) <- NA
max_cors <- apply(mat, 1, max, na.rm = TRUE)
min_cors <- apply(mat, 1, min, na.rm = TRUE)

p <- corrplot::corrplot(
  cors,
  method = 'ellipse',
  order = 'hclust',
  addrect = 2,
  type='full',
  diag=FALSE,
  addCoef.col = "black",
  number.cex = .75,
  tl.col="black",
  tl.pos = 'd',
  tl.cex = 0.75,
  p.mat = mat == max_cors | mat == min_cors,
  insig = "pch",
  pch = 0,
  pch.cex = 5,
  pch.col = "#D3D3D3"
)
```

## Couple & Sibling Pairs
```{r}
df <- cors_long %>%
  filter(pair_name %in% bookmaker_info$pair_name) %>%
  arrange(desc(cor)) %>%
  mutate(cor = scales::label_percent(accuracy=1)(cor))
row.names(df) <- df$Pair
df$Pair <- NULL

df %>%  
  kable(col.names = NULL) %>%
  kable_styling(full_width = FALSE)
```
